An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-12 EconGrowth2.Rnw
Now incorporating the CES spaghetti graph in the paper.

Figure~\ref{fig:CES_GDP_Lattice_Graph} compares CES model predictions 
to historical data for all nestings.

<<CES_GDP_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models.">>=
createCESLatticeGraph(energyType="Q")
@

The resample model predictions for each nesting 
in Figure~\ref{fig:CES_GDP_Lattice_Graph} can be shown as gray lines 
beneath superimposed on the historical data as shown
in Figures~\ref{fig:CES_Spaghetti_Graph_kl}--\ref{fig:CES_Spaghetti_Graph_ekl}. 
Figure~\ref{fig:CES_Spaghetti_Graph_kl} shows CES model resample predictions
for the ($kl$) nesting (without energy).

<<CES_Spaghetti_Graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$) nesting (without energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. Need to plot fit to historical data as a red line. Change vertical axis limits: China 1-10, all others 1-4. ****">>=
# For the data currently in the data_resample directory:
# data <- loadCESSpaghettiGraphData(energyType=NA)
# For the data in the n=50 archive:
data <- loadCESSpaghettiGraphData(energyType=NA, 
                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# For the data in the n=1000 archive:
# data <- loadCESSpaghettiGraphData(energyType=NA, 
#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
cesSpaghettiGraph(data=data)
@

Figure~\ref{fig:CES_Spaghetti_Graph_kle} shows CES model 
resample predictions for the ($kl$)$e$ nesting.

<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$)$e$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. Need to plot fit to historical data as a red line. Change vertical axis limits: China 1-10, all others 1-4. ****">>=
# For the data currently in the data_resample directory:
# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e")
# For the data in the n=50 archive:
data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e", 
                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# For the data in the n=1000 archive:
# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(kl)e",
#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
cesSpaghettiGraph(data=data)
@

<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($le$)$k$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. Need to plot fit to historical data as a red line. Change vertical axis limits: China 1-10, all others 1-4. ****">>=
# For the data currently in the data_resample directory:
# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k")
# For the data in the n=50 archive:
data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k", 
                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# For the data in the n=1000 archive:
# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(le)k",
#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
cesSpaghettiGraph(data=data)
@

<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($ek$)$l$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. Need to plot fit to historical data as a red line. Change vertical axis limits: China 1-10, all others 1-4. ****">>=
# For the data currently in the data_resample directory:
# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l")
# For the data in the n=50 archive:
data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l", 
                                  archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# For the data in the n=1000 archive:
# data <- loadCESSpaghettiGraphData(energyType="Q", nest="(ek)l",
#               archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
cesSpaghettiGraph(data=data)
@

>>>>

Figure~\ref{fig:CES_Spaghetti_Graph} compares CES model predictions 
to historical data for all nestings. 
Historical data are shown as open circles. 
The fit to historical data is shown as a dashed line. 
The gray band beneath the historical data shows the spread of predictions for 1000 resamples.

<<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
cesSpaghettiGraph(nest="all", energyType="Q")
@
